Research Notes

### 2020-07-07 notes/notes.tex
Wednesday notes
tuesday, june 30 notes
convert to MPI

>>>>

 \section{Wednesday, June 24}
    \begin{enumerate}

        \item Code
        \begin{enumerate}
            \item Parallelize
            \item Transition to numpy
        \end{enumerate}
        \item Theory Question
        \begin{enumerate}
            \item renormalize and regularlize: what do they mean?
            \item Look at LePage
        \end{enumerate}

 \section{Tuesday, June 30}
    \begin{enumerate}
        \item Code
        \begin{enumerate}
            \item Try \texttt{mpi4py}.
            \item Move to 3D (this may decrease parallel overhead)
        \end{enumerate}

        \item Reading
        \begin{enumerate}
            \item Continue Reading Collins, others. 
        \end{enumerate}
    \end{enumerate}

 \section{Thursday, July 2}
    \begin{enumerate}
        \item Coding
            \begin{enumerate}
                \item Continue implementing MPI
                \item Parallelization may be more apparent in 3D
            \end{enumerate}
        \item Reading
            \begin{enumerate }
                \item Dirac fermions, represented by 4D spinor field (spin up/down, electron/positron)    
                \item Look at Tong (Chap. 4)
                \item Charge (See Tong, Noether's Theorem)
            \end{enumerate}

        \item Next week back: start gradient flow on linear phi4 model
